%% Template for English Papers
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \documentclass[english]{jpnsecart}                   % English Original Paper

%% For JPNSEC office %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% You don't need to modify them. 
\received{2010}{8}{1}
\stuffincharge{XX\hspace{0.5zh} XX}
\setcounter{page}{1}
%\setcounter{volpage}{1}
\Vol{1}
\No{1}

%% CAUSION for amsmath package users %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \usepackpage{amsmath}
% equation No. should be reffered by the \eqref, not \ref
% specify the "fleqn" as the option of documentclass command
% ex. \documentclass[technicalpaper,fleqn]{jpnsecart}
%\usepackage{evocomp}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}


\usepackage{fancyhdr}
\usepackage{graphicx}
%\addcontentsline{toc}{chapter}{Bibliography}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{booktabs}
\usepackage{colortbl}


\newcommand{\gray}{\rowcolor[gray]{.90}}
\clubpenalty=10000
\widowpenalty=10000
\raggedbottom


%% Title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\etitle{MOEA/D-RAD - Resource Allocation by Diversity}
 \etitle[MOEA/D-RAD - Resource Allocation by Diversity]{MOEA/D-RAD - Resource Allocation by Diversity}
%\esubtitle{Resource Allocation by Diversity}

%% Authors %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% when authers whose affilication is the same is succeed, 
% use \affiliation macro for the top of the succeed authers 
% and use \sameaffiliation for the rest of the authors.
% Delete the following line if the number of author is less than four.
\manyauthor 
\author{%
	\name{Yuri}{Lavinas}
	\affiliation{University of Tsukuba, Graduate School of Systems and Information Engineering, Japan}%
	{yclavinas@gmail.com}
	\and
	\name{Claus}{Aranha}
	\sameaffiliation{caranha@cs.tsukuba.ac.jp}
%	\and
%	\name{Tetsuya}{Sakurai}
%	\sameaffiliation{sakurai@cs.tsukuba.ac.jp}
}

%% Keywords, Summary %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{keyword}
	resource allocation, diversity assessment, multiobjective optimization, priority functions.
\end{keyword}

\begin{summary}
	\input{0_abstract.tex}
\end{summary}


%% Body %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\maketitle
\footnotetext[1]{現職:進化計算研究所}
\setcounter{footnote}{1}

\input{1_intro.tex}
\input{2_stateoftheart.tex}
\input{3_method.tex}
\input{4_experimentaldesign.tex}
\input{5_results.tex}
\input{6_conclusion.tex}

\bibliography{btxsample}
\bibliographystyle{jpnsec}

%\appendix
%\section{Appendix}

%% Biography %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{biography}
	\profile{m}{Lavinas, Yuri}{Received his Bachelor degree from the University of Brasilia - Brazil, 2016, in Computer Science. Now he is pursuing his master degree in Computer Science on the University of Tsukuba - Japan. His research interests include Evolutionary Computation and optimization as well as Neuroevolution, and their applications.}%{portrait}
	
	\profile{m}{Aranha, Claus}{Obtained his PhD from the University of Tokyo, Graduate School of Frontier Sciences in 2010. From 2011 to 2012, was a Post-Doctoral Researcher at the COPPE School of Engineering, Federal University of Rio de Janeiro, Brasil. From 2012, is an Assistant Professor at the Faculty of Systems and Information Engineering, University of Tsukuba. His research interests include Auto-Adaptive Systems, applications of Evolutionary Computation, Computational Creativity, Multi Agent Systems and Artificial Life.}%{portrait}
\end{biography}


\end{document}
